---
title: "Graph generation with grapherator"
author: "Jakob Bossek"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Graph generation with grapherator}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>", warning = FALSE, message = FALSE)
options(tibble.print_min = 4L, tibble.print_max = 4L)
```

# Quickstart

The **grapherator** package for the statistical programming language [R](https://www.r-project.org) contains methods for benchmark instance generation of graph problems.

## Generating a benchmark instance

Here we first generate a bi-criteria graph problem with n = 25 nodes. The first objective is the euclidean distance of node coordinates in [0, 10] x [0, 10] in the euclidean plane. The second objective follows a normal distribution with mean 5 and standard deviation 1.5. The instance generation process is modular and thus highly flexible (see the [vignette on graph generation](Generation.html) for details).

```{r, fig.width=8, out.width='100%', fig.cap='Plot of the bi-objective sample graph `g.'}
library(mcMST)
library(gridExtra)
set.seed(1) # reproducability
g = mcGP(lower = 0, upper = 10)
g = addCoordinates(g, n = 25, generator = coordUniform)
g = addWeights(g, method = "euclidean")
g = addWeights(g, method = "random", weight.fun = rnorm, mean = 5, sd = 1.5)
print(g)
plots = plot(g)
plots$nrow = 1
do.call(grid.arrange, plots)
```
